---
title: "mlr3"
author: "Matt Dube"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: show
---

```{r setup, echo=TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```
## Setup

### Load Packages
```{r}
library(ggplot2)
library(ggthemes)
library(data.table)
library(mlr3)
library(mlr3viz)
```

### Load Data
```{r load_data}
customerDT <- fread(here::here("00_Data/raw", "WA_Fn-UseC_-Telco-Customer-Churn.csv"))
```

### Prep Data
```{r clean_data}
customerDT[,c("customerID", "TotalCharges", "gender", "PhoneService") := NULL][
    ,Churn := as.factor(Churn)][
      , SeniorCitizen := ifelse(SeniorCitizen == 1, "Yes", "No")]
```

## Create Task 
a new task is created with:
  `TaskClassif$new(id = "churn", backend = customerDT, target = "Churn", positive = "Yes")`
  
- id = "churn" --> task identifier, optional
- backend = customerDT --> backend sets the dataset for the task. 
- target = "Churn" --> target variable in the backend dataset 
- positive = "Yes" --> what factor of the target variable is the positive class

```{r create_task}
tsk_cust <- TaskClassif$new(id = "churn", backend = customerDT, target = "Churn", positive = "Yes")
```

### Review task
The created task is an R6 object. There are several methods that can be used to review the task details.

- `tsk_cust`
- `tsk_cust$ncol`
- `tsk_cust$nrow`
- `tsk_cust$feature_names`
- `tsk_cust$feature_types`
- `tsk_cust$col_roles`
- `tsk_cust$formula()`
- `tsk_cust$class_names`
- `tsk_cust$data()`

```{r review_task}
tsk_cust
tsk_cust$ncol
tsk_cust$nrow
tsk_cust$feature_names
tsk_cust$feature_types
tsk_cust$col_roles
tsk_cust$formula()
tsk_cust$class_names
tsk_cust$data()
```




